Viscous Transport in Eroding Porous Media

### 2019-09-30 docs/transport/erosion_transport.tex

Flow in porous media is further complicated when there is a two-way
coupling between the flow and the geometry. For example, the grains of a
porous media evolve in time in applications involving
melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
process that is prevalent in many geophysical, hydrological, and
industrial applications~\cite{berhanu2012shape, hewett2017evolution, lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.  When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.  For example, an eroded geometry may
contain channels of high porosity, which, though few in number and
modest in volume fraction, transmit a large portion of the flux. This
arrangement results in velocities that vary over several orders of
magnitude~\cite{all-hea-lab-rei2002}.  Moreover, channelization creates
a heterogeneous and anisotropic medium properties affecting the
transport of tracers such as contaminants~\cite{cve-che-wen1996,
dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.

This study consists of two main undertakings: first, high-fidelity
simulations of eroding porous media, and, second, characterizing
transport through the resulting geometries. Our modeling efforts build
on previous work~\cite{ris-moo-chi-she-zha2012, moore2013self, moo2017},
in particular recent numerical methods developed to simulate erosion in
the regime of Stokes flow~\cite{qua-moo2018}. We, however, make a few
key improvements to the numerical methods from~\cite{qua-moo2018} to
enable simulations of more realistic, dense suspensions of eroding
grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To
characterize transport in the resulting geometries, we examine
coarse-grained variables through statistical analysis of tracer
trajectories.

>>>>

%Flow in porous media is further complicated when there is a two-way coupling between the flow and the geometry. For example, the grains of a porous media evolve in time in applications involving
\nick{Flow in porous media is further complicated when boundaries evolve dynamically in response to the fluid flow. This type of coupling between geometry and flow occurs, for example, in applications involving} melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
process that is prevalent in many geophysical, hydrological, and
industrial applications~\cite{berhanu2012shape, hewett2017evolution, lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.  When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.  For example, an eroded geometry may
contain channels of high porosity, which, though few in number and
modest in volume fraction, transmit a large portion of the flux. This
arrangement results in velocities that vary over several orders of
magnitude~\cite{all-hea-lab-rei2002}.  \nick{Moreover, channelization creates heterogeneous and anisotropic medium properties, which affect the
transport of tracers} such as contaminants~\cite{cve-che-wen1996,
dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.

This study consists of two main undertakings: first, high-fidelity
simulations of eroding porous media, and, second, \nick{characterization of tracer transport through the dynamic geometries that result}. Our modeling efforts build on previous work~\cite{ris-moo-chi-she-zha2012, moore2013self, moo2017}, in particular recent numerical methods developed to simulate erosion in the regime of Stokes flow~\cite{qua-moo2018}. We, however, make a few
key improvements to the numerical methods from~\cite{qua-moo2018} to
enable simulations of more realistic, dense suspensions of eroding
grains (Figures~\ref{fig:Eroding50vel} and~\ref{fig:Eroding50vort}).  To characterize transport through these \nick{configurations}, we examine
coarse-grained variables through statistical analysis of tracer
trajectories.
